### 2013-07-23 doc/asplos14/overview.tex
added text to communication item on details

\item[Communication layer.] The main goal of our communication layer is to
aggregate small messages into large ones.  This process is invisible to the application
programmer. Its interface is based on active messages~\cite{vonEicken92}.
Since aggregation and deaggregation of messages needs to be very efficient, we perform the process in parallel and carefully use lock-free synchronization
operations.
\TODO{Re-include the mention of GASNET,MPI spawning,and inifiniband
    somewhere but not in the overview intro}

@@

>>>>

\item[Communication layer.] The main goal of our communication layer is to
aggregate small messages into large ones. This process is invisible to the
application programmer. Its interface is based on active
messages~\cite{vonEicken92}. Since aggregation and deaggregation of messages
needs to be very efficient, we perform the process in parallel and carefully
use lock-free synchronization operations.

GASNet~\cite{gasnet} is used as the
underlying mechanism for remote memory reads and writes using active message
invocations, with an off-the-shelf user-mode InfiniBand device driver
stack~\cite{OFED}. MPI is used for process setup and tear down.

@@

% \Grappa leverages as much freely available and commodity infrastructure as
% possible. We use unmodified Linux for the operating system and an
% off-the-shelf user-mode InfiniBand device driver stack~\cite{OFED}. MPI is
% used for process setup and tear down. GASNet~\cite{gasnet} is used as the
% underlying mechanism for remote memory reads and writes using active message
% invocations.
